---
title: "Prefered versus actual sentiment"
author: "Josephine Hillebrand Hansen"
date: "06/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





#Plot prefered sentiment against actual sentiment for beta 0 and LR 0
# Plot with and without sampling against each other.
```{r}
library(dplyr)
library(ggpubr)
data_noSample <- read.csv("experiment0_beta0_LR0_sampleFalse_22-08-2021 01-18-44.csv")
  
data_Sample <- read.csv("experiment2_beta0_16-08-2021 04-21-53.csv")



#split df into two in order to append sentiment2 and preferedsentiment 2 to the dfs.
data_noSample2 <- data_noSample %>%
  select(one_of("Sentiment2", "preferedSentiment2", "Agent2"))


data_noSample2 <- data_noSample2 %>%
  dplyr::rename(Sentiment1 = Sentiment2,
         preferedSentiment1 = preferedSentiment2,
         Agent1 = Agent2)

data_noSample <- rbind.fill(data_noSample, data_noSample2)


#The same for the data frame with sampling
data_Sample2 <- data_Sample %>%
  select(one_of("Sentiment2", "preferedSentiment2", "Agent2"))


data_Sample2 <- data_Sample2 %>%
  dplyr::rename(Sentiment1 = Sentiment2,
         preferedSentiment1 = preferedSentiment2,
         Agent1 = Agent2)

data_Sample <- rbind.fill(data_Sample, data_Sample2)



#Now create datatype column and bind the two.

data_noSample$sample = "Generation using beam search"
data_Sample$sample = "Generation using sampling"

data <- rbind(data_noSample, data_Sample)

data$sample <- factor(data$sample, levels = c("Generation using beam search", "Generation using sampling"))


#Create the plot
ggscatter(data, x = "preferedSentiment1", y = "Sentiment1", size = 0.6,
          color = "sample", palette = "jco",
          facet.by = "sample", #scales = "free_x",
          add = "reg.line", conf.int = TRUE,
          xlab = "Preferred sentiment",
          ylab = "Produced sentiment", fullrange = TRUE,
          title = "Preferred sentiment compared to produceed sentiment\n for chatbots using beam search and sampling") +
  stat_cor(aes(color = sample), method = "spearman", label.y = 1)



length(unique(data_noSample$Agent1))
length(unique(data_Sample$Agent1))



cor.test(data_Sample$preferedSentiment1, data_Sample$Sentiment1, method = c("spearman"))
```




#Look at how good the environment/algorithm is at figuring out the opinion of each chatbot
```{r}
data <- data_Sample[1:1250,]


empty_list <- vector(mode = "list", length = 0)


#okay, we have 50 chatbots.
#okay, we need to calculate the environment knowledge, which is given by:(t1*1+t2*2+...+t10*10)

#Let us loop through all and create an accumulated knowledge for each chatbot at each step?
data$knowledge1 = NA
data$knowledge2 = NA

data$interaction1 = NA
data$interaction2 = NA
for (i in 1:length(unique(data$Id))){
  print(i)
  temp = list(0)
  interaction = 1
  for (j in 1:nrow(data)){
    
    if (data$Id[j] == i){
      
      knowledge = weighted.mean(unlist(temp), 1:length(temp))
      
      temp <- append(temp, data$Sentiment1[j])
      
      data$knowledge1[j] = knowledge
      data$interaction1[j] = interaction
      interaction = interaction + 1
    }
    if (data$Partner_ID[j] == i){
      
      knowledge = weighted.mean(unlist(temp), 1:length(temp))
      
      temp <- append(temp, data$Sentiment2[j])
      
      data$knowledge2[j] = knowledge
      data$interaction2[j] = interaction
      
      interaction = interaction + 1
    }
    if (length(temp) > 10){
      temp[1] = NULL
    }
}}



#now bind them below each other.
data2 <- data %>%
  dplyr::select(one_of("Sentiment2", "preferedSentiment2", "Agent2", "knowledge2", "Step", "interaction2"))


data2 <- data2 %>%
  dplyr::rename(Sentiment1 = Sentiment2,
         preferedSentiment1 = preferedSentiment2,
         Agent1 = Agent2,
         knowledge1 = knowledge2,
         interaction1 = interaction2)

data <- rbind.fill(data, data2)



#Now create a plot
ggpar(ggscatter(data, x = "preferedSentiment1", y = "knowledge1", size = 0.6,
          palette = "jco",
          add = "reg.line", conf.int = TRUE,
          xlab = "Preferred opinion",
          ylab = "Inferred opinion",
          fullrange = TRUE), xlim=c(-1,1), fullrange = TRUE, title ="Correlation between inferred opinion and preferred\nopinion") +
  stat_cor(method = "spearman", label.y = 1)


ggpar(ggscatter(data[data$Step > 5,], x = "preferedSentiment1", y = "knowledge1", size = 0.6,
          palette = "jco",
          add = "reg.line", conf.int = TRUE,
          xlab = "Preferred sentiment",
          ylab = "Inferred opinion",
          fullrange = TRUE), xlim=c(-1,1), fullrange = TRUE) +
  stat_cor(method = "spearman", label.y = 1)

#After each chatbot has had 10 interactions
ggpar(ggscatter(data[data$interaction1 > 10,], x = "preferedSentiment1", y = "knowledge1", size = 0.6,
          palette = "jco",
          add = "reg.line", conf.int = TRUE,
          xlab = "Preferred opinion",
          ylab = "Inferred opinion",
          fullrange = TRUE), xlim=c(-1,1), fullrange = TRUE, title ="Correlation between inferred opinion and preferred\nopinion after 10 steps") +
  stat_cor(method = "spearman", label.y = 1)




#look at correlation per time step:

correlations = ddply(data, "Step", summarise, corr=cor(preferedSentiment1, knowledge1))

ggpar(ggscatter(correlations, x = "Step", y = "corr", size = 2,
          palette = "jco",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Step",
          title = "Correlation between preferred opinion and inferred opinion\nas a function of steps",
          ylab = "Correlation between preferred opinion and inferrred opinion",
          fullrange = TRUE), ylim = c(0,1),fullrange = TRUE)


#look at correlation per interaction:
correlations = ddply(data, "interaction1", summarise, corr=cor(preferedSentiment1, knowledge1))

ggpar(ggscatter(correlations[correlations$interaction1 < 56,], x = "interaction1", y = "corr", size = 2,
          palette = "jco",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Interaction",
          title = "Correlation between preferred opinion and inferred opinion\nas a function of interactions",
          ylab = "Correlation between preferred opinion and inferrred opinion",
          fullrange = TRUE), ylim = c(0,1),fullrange = TRUE)

```













#Read in data for all beta experiments (with no learning rate)
create column for beta.
rbind the dataframes.
compare prefered sentiments - that is how similar are the agents who interact with each other.
```{r}
databeta1 <- read.csv("experiment2_beta0.5_17-08-2021 10-18-00.csv")
databeta2 <- read.csv("experiment2_beta0_16-08-2021 04-21-53.csv")
databeta3 <- read.csv("experiment2_beta1_15-08-2021 14-48-24.csv")
databeta4 <- read.csv("experiment2_beta2_16-08-2021 19-47-29.csv")
databeta5 <- read.csv("experiment2_beta3_17-08-2021 23-26-45.csv")


databeta1$beta = 0.5
databeta2$beta = 0
databeta3$beta = 1
databeta4$beta = 2
databeta5$beta = 3


data <- rbind(databeta1, databeta2, databeta3, databeta4, databeta5)

data$beta <- as.factor(data$beta)


#Create the plot
ggscatter(data, x = "preferedSentiment1", y = "preferedSentiment2", size = 0.6,
          color = "beta", palette = "jco",
          facet.by = "beta", #scales = "free_x",
          add = "reg.line", conf.int = TRUE,
          xlab = "Preferred sentiment",
          ylab = "Preferred sentiment partner", fullrange = TRUE) +
  stat_cor(aes(color = beta), method = "spearman", label.y = 1.1)

ggscatter(data[data$Step > 3,], x = "preferedSentiment1", y = "preferedSentiment2", size = 0.6,
          color = "beta", palette = "jco",
          facet.by = "beta", #scales = "free_x",
          add = "reg.line", conf.int = TRUE,
          xlab = "Preferred opinion",
          ylab = "Preferred opinion partner", fullrange = TRUE,
          title = "Correlation between preferred opinion and preferred opinion\nof the partner divided by beta") +
  stat_cor(aes(color = beta), method = "spearman", label.y = 1)

```







#learning rate experiments - read in learning data and compare the developments of the system
```{r}
dataLR1 <- read.csv("experiment2_beta0_16-08-2021 04-21-53.csv")
dataLR2 <- read.csv("experiment3_beta0_LR0.1_18-08-2021 12-39-25.csv")
dataLR3 <- read.csv("experiment3_beta0_LR0.5_19-08-2021 00-56-25.csv")
dataLR4 <- read.csv("experiment0_beta0_LR0.05_26-08-2021 10-05-58.csv")
dataLR5 <- read.csv("experiment3_beta0_LR0.3_24-08-2021 16-44-33.csv")
dataLR6 <- read.csv("experiment3_beta0_LR0.7_26-08-2021 22-40-18.csv")
dataLR7 <- read.csv("experiment0_beta0_LR1_27-08-2021 12-07-57.csv")

dataLR1$LR = 0
dataLR2$LR = 0.1
dataLR3$LR = 0.5
dataLR4$LR = 0.05
dataLR5$LR = 0.3
dataLR6$LR = 0.7
dataLR7$LR = 1

#LR1
dataLR1_2 <- dataLR1 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR1_2 <- dataLR1_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

dataLR1 <- rbind.fill(dataLR1, dataLR1_2)

#LR2
dataLR2_2 <- dataLR2 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR2_2 <- dataLR2_2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)

dataLR2 <- rbind.fill(dataLR2, dataLR2_2)

#LR3
dataLR3_2 <- dataLR3 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR3_2 <- dataLR3_2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)

dataLR3 <- rbind.fill(dataLR3, dataLR3_2)

#LR4
dataLR4_2 <- dataLR4 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR4_2 <- dataLR4_2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)

dataLR4 <- rbind.fill(dataLR4, dataLR4_2)

#LR5
dataLR5_2 <- dataLR5 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR5_2 <- dataLR5_2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)

dataLR5 <- rbind.fill(dataLR5, dataLR5_2)

#LR6
dataLR6_2 <- dataLR6 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR6_2 <- dataLR6_2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)

dataLR6 <- rbind.fill(dataLR6, dataLR6_2)

#LR7
dataLR7_2 <- dataLR7 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR7_2 <- dataLR7_2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)

dataLR7 <- rbind.fill(dataLR7, dataLR7_2)



dataLR <- rbind(dataLR1, dataLR2, dataLR3, dataLR4, dataLR5, dataLR6, dataLR7)

dataLR$LR <- as.factor(dataLR$LR)

ggscatter(dataLR, x = "Step", y = "preferedSentiment1", size = 0.6,
          color = "LR", palette = "jco",
          facet.by = "LR", #scales = "free_x",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred opinion", fullrange = TRUE,
          title = "Preferred opinion as a function of steps split by learning rate")



```






#experiment 3 - combination of LR and beta
```{r}
datae3_1 = read.csv("experiment3_beta0_LR0.1_18-08-2021 12-39-25.csv")
datae3_2 = read.csv("experiment3_beta1_LR0.1_19-08-2021 13-13-51.csv")
datae3_3 = read.csv("experiment3_beta2_LR0.1_20-08-2021 14-39-25.csv")
datae3_4 = read.csv("experiment3_beta3_LR0.1_21-08-2021 04-16-52.csv")

datae3_1$beta = 0
datae3_2$beta = 1
datae3_3$beta = 2
datae3_4$beta = 3

#e3_1
datae3_1_2 <- datae3_1 %>% 
  select(one_of("preferedSentiment2","beta", "Step"))
datae3_1_2 <- datae3_1_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

datae3_1 <- rbind.fill(datae3_1, datae3_1_2)

#e3_2
datae3_2_2 <- datae3_2 %>% 
  select(one_of("preferedSentiment2","beta", "Step"))
datae3_2_2 <- datae3_2_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

datae3_2 <- rbind.fill(datae3_2, datae3_2_2)


#e3_3
datae3_3_2 <- datae3_3 %>% 
  select(one_of("preferedSentiment2","beta", "Step"))
datae3_3_2 <- datae3_3_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

datae3_3 <- rbind.fill(datae3_3, datae3_3_2)

#e3_4
datae3_4_2 <- datae3_4 %>% 
  select(one_of("preferedSentiment2","beta", "Step"))
datae3_4_2 <- datae3_4_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

datae3_4 <- rbind.fill(datae3_4, datae3_4_2)


datae3 <- rbind(datae3_1,datae3_2,datae3_3,datae3_4)

datae3$beta <- as.factor(datae3$beta)



ggscatter(datae3, x = "Step", y = "preferedSentiment1", size = 0.6,
          color = "beta", palette = "jco",
          facet.by = "beta", #scales = "free_x",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred opinion",
          title = "Preferred opinion as a function of steps for different beta\nvalues when learning rate is 0.1", fullrange = TRUE)




data <- read.csv("experiment3_beta3_LR0.05_21-08-2021 21-36-55.csv")


data2 <- data %>%
  select(one_of("Step", "preferedSentiment2"))

data2 <- data2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)


data <- rbind.fill(data, data2)



ggscatter(data, x = "Step", y = "preferedSentiment1", size = 0.6,
          palette = "jco",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred sentiment", fullrange = TRUE)







#With 50 steps
data <- read.csv("experiment0_beta3_LR0.05_50steps_23-08-2021 21-58-44.csv")


data2 <- data %>%
  select(one_of("Step", "preferedSentiment2"))

data2 <- data2 %>%
  dplyr::rename(preferedSentiment1 = preferedSentiment2)


data <- rbind.fill(data, data2)



ggscatter(data, x = "Step", y = "preferedSentiment1", size = 0.6,
          palette = "jco",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred sentiment", fullrange = TRUE)



#Look also at communities formed
data <- read.csv("experiment0_beta3_LR0.05_50steps_23-08-2021 21-58-44.csv")
data = data[data$Step > 45,]
relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]

net <- graph_from_data_frame(d = data[,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)


```


#Look at data run for 100 steps for beta = 3 and beta = 2 with LR = 0.1
```{r}
#DataLR 100
dataLR100 <- read.csv("experiment100_beta3_LR0.1_27-08-2021_12-09-19.csv")


dataLR100_2 <- dataLR100 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR100_2 <- dataLR100_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

dataLR100 <- plyr::rbind.fill(dataLR100, dataLR100_2)


ggscatter(dataLR100, x = "Step", y = "preferedSentiment1", size = 0.6,
          palette = "jco",
          #facet.by = "LR", #scales = "free_x",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred opinion", fullrange = TRUE,
          title ="Preferred opinion as a function of steps for beta = 3\nand learning rate = 0.1")


```


```{r}


dataLR100 <- read.csv("experiment_beta2_LR0.1_28-08-2021_05-19-23.csv")


dataLR100_2 <- dataLR100 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR100_2 <- dataLR100_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

dataLR100 <- plyr::rbind.fill(dataLR100, dataLR100_2)


ggscatter(dataLR100, x = "Step", y = "preferedSentiment1", size = 0.6,
          palette = "jco",
          #facet.by = "LR", #scales = "free_x",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred opinion", fullrange = TRUE,
          title ="Preferred opinion as a function of steps for beta = 2\nand learning rate = 0.1")
```




#Visualize networks from beta experiment
```{r}
library(igraph)
library(dplyr)
library(scales)

data = read.csv("experiment2_beta3_17-08-2021 23-26-45.csv")

relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]

net <- graph_from_data_frame(d = data[data$Step >= 4,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)
plot(net2, vertex.label=NA,layout = layout_nicely)


net2 <- simplify(net)
E(net2)$weight = sapply(E(net2), function(e) { 
    length(all_shortest_paths(net, from=ends(net2, e)[1], to=ends(net2, e)[2])$res)/2 } )
plot(net2, 
     vertex.size=15, 
     vertex.label.dist=0.5, 
     vertex.label.cex=0.8,
     vertex.label.degree=-pi/2, 
     edge.width=E(net2)$weight,
     layout=layout_nicely,
     margin=-0.2,
     vertex.label = NA)
```



#Beta2
```{r}

data = read.csv("experiment2_beta2_16-08-2021 19-47-29.csv")

relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]


net <- graph_from_data_frame(d = data[data$Step >= 4,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)
plot(net2, vertex.label=NA,layout = layout_nicely)


net2 <- simplify(net)
E(net2)$weight = sapply(E(net2), function(e) { 
    length(all_shortest_paths(net, from=ends(net2, e)[1], to=ends(net2, e)[2])$res)/2 } )
plot(net2, 
     vertex.size=15, 
     vertex.label.dist=0.5, 
     vertex.label.cex=0.8,
     vertex.label.degree=-pi/2, 
     edge.width=E(net2)$weight,
     layout=layout_nicely,
     margin=-0.2,
     vertex.label = NA)
```




```{r}

data = read.csv("experiment2_beta1_15-08-2021 14-57-37.csv")

relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]


net <- graph_from_data_frame(d = data[data$Step >= 4,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)
plot(net2, vertex.label=NA,layout = layout_nicely)


net2 <- simplify(net)
E(net2)$weight = sapply(E(net2), function(e) { 
    length(all_shortest_paths(net, from=ends(net2, e)[1], to=ends(net2, e)[2])$res)/2 } )
plot(net2, 
     vertex.size=15, 
     vertex.label.dist=0.5, 
     vertex.label.cex=0.8,
     vertex.label.degree=-pi/2, 
     edge.width=E(net2)$weight,
     layout=layout_nicely,
     margin=-0.2,
     vertex.label = NA)
```




```{r}

data = read.csv("experiment2_beta0_16-08-2021 04-21-53.csv")

relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]


net <- graph_from_data_frame(d = data[data$Step >= 4,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)
plot(net2, vertex.label=NA,layout = layout_nicely)


net2 <- simplify(net)
E(net2)$weight = sapply(E(net2), function(e) { 
    length(all_shortest_paths(net, from=ends(net2, e)[1], to=ends(net2, e)[2])$res)/2 } )
plot(net2, 
     vertex.size=15, 
     vertex.label.dist=0.5, 
     vertex.label.cex=0.8,
     vertex.label.degree=-pi/2, 
     edge.width=E(net2)$weight,
     layout=layout_nicely,
     margin=-0.2,
     vertex.label = NA)
```







```{r}

data = read.csv("experiment2_beta0.5_17-08-2021 10-18-00.csv")

relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]


net <- graph_from_data_frame(d = data[data$Step >= 4,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)
plot(net2, vertex.label=NA,layout = layout_nicely)


net2 <- simplify(net)
E(net2)$weight = sapply(E(net2), function(e) { 
    length(all_shortest_paths(net, from=ends(net2, e)[1], to=ends(net2, e)[2])$res)/2 } )
plot(net2, 
     vertex.size=15, 
     vertex.label.dist=0.5, 
     vertex.label.cex=0.8,
     vertex.label.degree=-pi/2, 
     edge.width=E(net2)$weight,
     layout=layout_nicely,
     margin=-0.2,
     vertex.label = NA)
```








#Split out on first 5 and last time steps to inspect the network.

```{r}

data = read.csv("experiment2_beta1_15-08-2021 14-57-37.csv")
data = data[data$Step >20,]


relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]

net <- graph_from_data_frame(d = data[,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)
plot(net2, vertex.label=NA,layout = layout_nicely)


net2 <- simplify(net)
E(net2)$weight = sapply(E(net2), function(e) { 
    length(all_shortest_paths(net, from=ends(net2, e)[1], to=ends(net2, e)[2])$res)/2 } )
plot(net2, 
     vertex.size=15, 
     vertex.label.dist=0.5, 
     vertex.label.cex=0.8,
     vertex.label.degree=-pi/2, 
     edge.width=E(net2)$weight,
     layout=layout_nicely,
     margin=-0.2,
     vertex.label = NA)
```



























































#Graphs for a 100 interactions with beta = 3
```{r}
dataLR100 <- read.csv("experiment100_beta3_LR0.1_27-08-2021_12-09-19.csv")


data = dataLR100[dataLR100$Step >=91 & dataLR100$Step <= 100,]


relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]

net <- graph_from_data_frame(d = data[,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)

```



```{r}


dataLR100 <- read.csv("experiment_beta2_LR0.1_28-08-2021_05-19-23.csv")


data = dataLR100[dataLR100$Step >=91 & dataLR100$Step <= 100,]


relations <-data %>%
  select(one_of("Id", "preferedSentiment1"))
relations <- relations[!duplicated(relations$Id), ]

net <- graph_from_data_frame(d = data[,c("Id", "Partner_ID")], directed = FALSE, vertices = relations)


V(net)$value <- relations$preferedSentiment1
#V(net)$col_values <- round( rescale(V(net)$value, to = c(1,100)),0)
V(net)$col_values <- ceiling((V(net)$value+1)/2*100)

# Colour vertecies
colours <- colorRampPalette(c("gray80", "red"))(100)
V(net)$color <- colours[ V(net)$col_values ]

# Color edges
E(net)$color <- "black"

#Highlight edge
E(net)$width <- 1
E(net)$width[5] <- 5

# Plot
plot(net)

#Remove vertex labels
plot(net, vertex.label=NA,layout = layout_nicely)


```








#polarization experiment
```{r}


dataLR100 <- read.csv("experiment_polarization_beta0_LR0.1_29-08-2021_21-26-45.csv")


dataLR100_2 <- dataLR100 %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataLR100_2 <- dataLR100_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

dataLR100 <- plyr::rbind.fill(dataLR100, dataLR100_2)


ggscatter(dataLR100, x = "Step", y = "preferedSentiment1", size = 0.6,
          palette = "jco",
          #facet.by = "LR", #scales = "free_x",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred opinion", fullrange = TRUE,
          title ="Preferred opinion as a function of steps for beta = 0\nand learning rate = 0.1")
```



#polarization experiment
```{r}


dataPolarization <- read.csv("experiment_polarization_beta3_LR0.1_29-08-2021_17-02-13.csv")


dataPolarization_2 <- dataPolarization %>% 
  select(one_of("preferedSentiment2","LR", "Step"))
dataPolarization_2 <- dataPolarization_2 %>%
  dplyr::rename(preferedSentiment1=preferedSentiment2)

dataPolarization <- plyr::rbind.fill(dataPolarization, dataPolarization_2)


ggscatter(dataPolarization, x = "Step", y = "preferedSentiment1", size = 0.6,
          palette = "jco",
          #facet.by = "LR", #scales = "free_x",
          #add = "reg.line", conf.int = TRUE,
          xlab = "Steps",
          ylab = "Preferred opinion", fullrange = TRUE,
          title ="Preferred opinion as a function of steps for beta = 3\nand learning rate = 0.1")
```
